The evolution of the transcriptome of mammalian placentas

### 2016-09-12 manuscript/manuscript.Rnw
rewrite introduction

>>>>

The placenta is arguably one of the most variable organs in different
species of mammals in terms of the shape of attachment
(\Sexpr{english.join(placenta_classification[,levels(as.factor(shape))])}),
degree of intimacy between fetal tissues and maternal tissues
(\Sexpr{english.join(placenta_classification[,levels(as.factor(intimacy))])}),
and degree of interdigitation of maternal and fetal tissues
(\Sexpr{english.join(placenta_classification[,levels(as.factor(interdigitation))])})
while its primary functions (transfer of nutrients and oxygen to the
fetus, removal of wastes and carbon dioxide) are strongly conserved.
